Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-06 R0V0.tex
Add definition of undirected and directed graphs
Change the location of the communication graph to before the problem formulation

\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node.

@@

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}$ defined by the set of vertices $\mathscr{V}=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.

@@

\mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the set $\mathscr{K}$. The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$, for instance, it can be described by a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ that defined the communication network among different controllers.

>>>>

\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. A graph is said to be \emph{undirected} if, for every edge $(i,j)\in\mathscr{E}$, there exists $(j,i)\in\mathscr{E}$. It is said to be \emph{directed} if otherwise. Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node.

@@

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}$ defined by the set of vertices $\mathscr{V}=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network, for each $i\in\mathscr{V}$, define the set $\mathscr{K}(i)=\{j\in\mathbb{N}_{[1,N]}:(i,j)\in\mathscr{E}_c\}$. One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{K}$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_k$ for which $k\in\mathscr{K}(i)$.

@@

\mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the set $\mathscr{K}$.
